The Dark \LaTeX{} \\ \large An Example of the dndbook Class

### 2021-01-04 example.tex
New command \tocside adds sidebar entry to table of contents
Support for multiple maps using \DndMap{title} and \ref{map:title}

@@

@@

\begin{DndSidebar}[float=!b]{Behold the DndSidebar!}
  The |DndSidebar| is used as a sidebar. It does not break over columns and is best used with a figure environment to float it to one corner of the page where the surrounding text can then flow around it.
\end{DndSidebar}

>>>>

The command |\DndMap{title}| creates a new map index (A, B, C\ldots). This doesn't add anything to the document, but the map index can be referenced with |\ref{map:title}|. For example, the Kingdom is map\,\ref{map:The Kingdom}.

\DndMap{The Kingdom}

Areas can be references with |\ref{area:name}|. For example, Mount Doofus is area \ref{area:Mount Doofus}.

@@

\section{Map References}

\DndArea[\ref{map:The Kingdom}]{Mount Doofus}
This area has a prefix before the number. The prefix is an optional parameter on |\DndArea|. Useful if your document contains multiple maps!

@@

\begin{DndSidebar}[float=!b]{Behold the DndSidebar!}
\tocside{Behold the DndSidebar!}
  The |DndSidebar| is used as a sidebar. It does not break over columns and is best used with a figure environment to float it to one corner of the page where the surrounding text can then flow around it.

  Use the |\tocside{title}| command to create an entry in the table of contents, if you want.
\end{DndSidebar}
